Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface

### 2022-05-25 assets/tag_distribution.tex
:paintbrush: Add probability and block illustrations

\begin{tikzpicture}
	\begin{groupplot}
		[group style={%
					rows=3,
					group name=plots,
					x descriptions at=edge bottom,
					y descriptions at=edge left,
					vertical sep=15
				},
			ybar,
			xmin=0,
			xmax=4,
			xtick={1,2,3,4},
			ymin=0,
			ymax=1,
			xlabel={Reflection State},
			ylabel={Probability},
			enlarge x limits={value=0.25,upper},
			enlarge y limits={value=0.1,upper},
			width=10cm,
			height=4cm,
			every axis plot/.append style={bar shift=0},
			legend style={pattern=none}
		]
		\nextgroupplot
		\addplot[blue,fill=blue!30!white] coordinates {(-1,-1)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0.25)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,0.25)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.25)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0.25)};
		\legend{SR}
		\nextgroupplot
		\addplot[red,fill=red!30!white] coordinates {(-1,-1)};
		\addplot[red,fill=red!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0)};
		\addplot[red,fill=red!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,1)};
		\addplot[red,fill=red!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0)};
		\addplot[red,fill=red!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0)};
		\legend{IRS}
		\nextgroupplot
		\addplot[brown,fill=brown!30!white] coordinates {(-1,-1)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0.2)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,0.4)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.3)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0.1)};
		\legend{Metascatter}
	\end{groupplot}
\end{tikzpicture}

>>>>

\begin{tikzpicture}
	\begin{groupplot}
		[group style={%
					rows=3,
					group name=plots,
					x descriptions at=edge bottom,
					y descriptions at=edge left,
					vertical sep=15
				},
			ybar,
			xmin=0,
			xmax=4,
			xtick={1,2,3,4},
			ymin=0,
			ymax=1,
			xlabel={Reflection State},
			ylabel={Probability},
			enlarge x limits={value=0.25,upper},
			enlarge y limits={value=0.1,upper},
			width=10cm,
			height=4cm,
			every axis plot/.append style={bar shift=0},
			legend style={pattern=none}
		]
		\nextgroupplot
		\addplot[blue,fill=blue!30!white] coordinates {(-1,-1)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0.25)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,0.25)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.25)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0.25)};
		\legend{SR}
		\nextgroupplot
		\addplot[red,fill=red!30!white] coordinates {(-1,-1)};
		\addplot[red,fill=red!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0)};
		\addplot[red,fill=red!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,1)};
		\addplot[red,fill=red!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0)};
		\addplot[red,fill=red!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0)};
		\legend{IRS}
		\nextgroupplot
		\addplot[brown,fill=brown!30!white] coordinates {(-1,-1)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0.125)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,0.625)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.25)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0)};
		\legend{Metascatter}
	\end{groupplot}
\end{tikzpicture}

### 2022-05-25 main.tex
:paintbrush: Add probability and block illustrations

		\begin{figure}[!t]
			\centering
			\resizebox{0.95\columnwidth}{!}{
				\begin{tikzpicture}
					\begin{groupplot}
						[group style={%
									rows=3,
									group name=plots,
									x descriptions at=edge bottom,
									y descriptions at=edge left,
									vertical sep=15
								},
							ybar,
							xmin=0,
							xmax=4,
							xtick={1,2,3,4},
							ymin=0,
							ymax=1,
							xlabel={Reflection State},
							ylabel={Probability},
							enlarge x limits={value=0.25,upper},
							enlarge y limits={value=0.1,upper},
							width=10cm,
							height=4cm,
							every axis plot/.append style={bar shift=0},
							legend style={pattern=none}
						]
						\nextgroupplot
						\addplot[blue,fill=blue!30!white] coordinates {(-1,-1)};
						\addplot[blue,fill=blue!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0.25)};
						\addplot[blue,fill=blue!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,0.25)};
						\addplot[blue,fill=blue!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.25)};
						\addplot[blue,fill=blue!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0.25)};
						\legend{SR}
						\nextgroupplot
						\addplot[red,fill=red!30!white] coordinates {(-1,-1)};
						\addplot[red,fill=red!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0)};
						\addplot[red,fill=red!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,1)};
						\addplot[red,fill=red!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0)};
						\addplot[red,fill=red!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0)};
						\legend{IRS}
						\nextgroupplot
						\addplot[brown,fill=brown!30!white] coordinates {(-1,-1)};
						\addplot[brown,fill=brown!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0.2)};
						\addplot[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,0.4)};
						\addplot[brown,fill=brown!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.3)};
						\addplot[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0.1)};
						\legend{Metascatter}
					\end{groupplot}
				\end{tikzpicture}
			}
		\end{figure}

>>>>

		\begin{figure}[!t]
			\centering
			\resizebox{0.95\columnwidth}{!}{
				\begin{tikzpicture}
					\begin{groupplot}
						[group style={%
									rows=3,
									group name=plots,
									x descriptions at=edge bottom,
									y descriptions at=edge left,
									vertical sep=15
								},
							ybar,
							xmin=0,
							xmax=4,
							xtick={1,2,3,4},
							ymin=0,
							ymax=1,
							xlabel={Reflection State},
							ylabel={Probability},
							enlarge x limits={value=0.25,upper},
							enlarge y limits={value=0.1,upper},
							width=10cm,
							height=4cm,
							every axis plot/.append style={bar shift=0},
							legend style={pattern=none}
						]
						\nextgroupplot
						\addplot[blue,fill=blue!30!white] coordinates {(-1,-1)};
						\addplot[blue,fill=blue!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0.25)};
						\addplot[blue,fill=blue!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,0.25)};
						\addplot[blue,fill=blue!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.25)};
						\addplot[blue,fill=blue!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0.25)};
						\legend{SR}
						\nextgroupplot
						\addplot[red,fill=red!30!white] coordinates {(-1,-1)};
						\addplot[red,fill=red!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0)};
						\addplot[red,fill=red!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,1)};
						\addplot[red,fill=red!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0)};
						\addplot[red,fill=red!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0)};
						\legend{IRS}
						\nextgroupplot
						\addplot[brown,fill=brown!30!white] coordinates {(-1,-1)};
						\addplot[brown,fill=brown!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0.125)};
						\addplot[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,0.625)};
						\addplot[brown,fill=brown!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.25)};
						\addplot[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0)};
						\legend{Metascatter}
					\end{groupplot}
				\end{tikzpicture}
			}
		\end{figure}
